TBD

### 2021-03-18 outputs/paper/paper.Rmd
bib updates w/o tidyverse

We replicate this paper using R statistical programming language [@citeR]. In particular, we use packages `tidyverse` [@citetidyverse],  `here` [@citehere], `ggpubr` [@citeggpubr] to manipulate data and packages, `kableExtra` [@citekableExtra] to generate tables, and `ggplot2` [@citeggplot], `ggthemes` [@citeggthemes] to adjust diagrams themes.

>>>>

We replicate this paper using R statistical programming language [@citeR]. In particular, we use packages `tidyverse` [@citeTidyverse],  `here` [@citehere], `ggpubr` [@citeggpubr] to manipulate data and packages, `kableExtra` [@citekableExtra] to generate tables, and `ggplot2` [@citeggplot], `ggthemes` [@citeggthemes] to adjust diagrams themes.
